---
title: "Month9Week4_Slides"
author: "Morne Grewar"
date: "25/04/2020"
output: ioslides_presentation
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## Main page of application

The main page of the application shows the required inputs and give the output from the model with a graph to show the original data. The code for the regression model is shown below

```{r main, echo = TRUE,eval=FALSE}
model<- train(as.factor(Species)~.,data=iris,method="rf",
              trControl=trainControl(method="cv", number=5, verboseIter=F))
```

## Model accuracy and outputs

The model resuslts are shown below, here it can be seen that the model has an 95% accuracy

```{r model, echo = FALSE}
suppressMessages(suppressWarnings(library(caret)))
set.seed(2)
model<- train(as.factor(Species)~.,data=iris,method="rf",
              trControl=trainControl(method="cv", number=5, verboseIter=F))
```

```{r model2, echo = TRUE}
model$results
```

## Some info about the model data

The iris dataset is included in the datasets library, with the following properties it is a data frame with 150 cases (rows) and 5 variables (columns) named Sepal.Length, Sepal.Width, Petal.Length, Petal.Width, and Species. The structure of the dataset is shown below

```{r data, echo = FALSE}
str(iris)
```


## Link to shiny app on server

A screen shot of the app is shown below. The link to the app is <http://mggshiny.shinyapps.io/month9week4_project2> 

```{r picture,echo = FALSE}
library(jpeg)
library(grid)
img<- readJPEG("C:/Users/Morne Grewar/Documents/Coursera Course/Month 9/Week 4/Capture.jpg")
grid.raster(img,just = "centre")
```





